We are not the 99 percent: quantifying bright satellite distributions in the Local Group

### 2017-11-01 paper/paper.tex
+1 paragraph

>>>>

The right panel shows the normalized results. 
This highlights the two results mentioned above.
First, the MW shows a low $c/a$ ration $2.5$ standard deviations away
from the mean value of the spherical distribution; this contrasts the
results for M31 which are close to $1$ standard deviation away.
Second, the less massive halos in the Illustris simulation present a
smaller dispersion in their deviations from sphericity than the
its masssive partner.

These
